Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-09-23 manuscript.tex
overleaf update

\hypertarget{fig:figurename2}{%
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{./figs_03/fig_intro_light.pdf}
\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation. An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data. b) Diagram of the expiremental setup. WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
\label{fig:figurename2}
\end{figure}
}

@@

>>>>

\hypertarget{fig:intro}{%
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_light.pdf}
\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation. An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data. b) Diagram of the expiremental setup. WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
\label{fig:intro}
\end{figure}
}

@@

\hypertarget{fig:waveform}{%
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{./figs_03/waveform_light.pdf}
\caption[{PNR-sensitive Pulse Waveform}]{\textbf{PNR-sensitive Pulse Waveform} The rising edge of the differential SNSPD's RF pulses exibit variations in height, slew rate, and arrival time due to photon-number dependent dynamics. The slopes of the 1-photon and 2-photon pulses significantly differ, and as the photon number increases, the alterations to the pulse shape become progressively smaller. Trigger levels A (8~mV) and B (50~mV) were used to extract as much information about pulse slope and arrival time as possible}
\label{fig:waveform}
\end{figure}
}
